DOM bridges and barriers: systematic review and survey

### 2025-11-25 reports/draft_results.qmd
positron

consv_bar <- ggplot(consv_s) +
  geom_bar(aes(x = perc, y = reorder(consv_topic, perc)), fill = "dodgerblue4", width = 0.6, stat = "identity")+
  scale_x_continuous(position = "top", 
                     expand = c(0,0), 
                     limits = c(0, 45))+
  scale_y_discrete(expand = expansion(add = c(0,0))) + 
  theme(
    # Set background color to white
    panel.background = element_rect(fill = "white"),
    # Set the color and the width of the grid lines for the horizontal axis
    panel.grid.major.x = element_line(color = "#A8BAC4", size = 0.3),
    # Remove tick marks by setting their length to 0
    axis.ticks.length = unit(0, "mm"),
    # Remove the title for both axes
    axis.title = element_blank(),
    # Only left line of the vertical axis is painted in black
    axis.line.y.left = element_line(color = "black"),
    # Remove labels from the vertical axis
    axis.text.y = element_blank(),
    # But customize labels for the horizontal axis
    axis.text.x = element_text(family = "Arial", size = 12)) + 
  geom_text(aes(x = perc, y = consv_topic, label = consv_topic),
    hjust = 0,
    nudge_x = 0.3,
    colour = "dodgerblue4",
    family = "Arial",
    size = 3.5)+
  labs(subtitle = "Percent of sum from all articles (%)") + 
  theme(plot.subtitle = element_text(
      family = "Arial",
      size = 13)
  )

consv_bar
```

@@

consv_bar2 <- ggplot(consv_s) +
  geom_bar(aes(x = perc, y = reorder(consv_bin, perc), fill = consv_topic), width = 0.6, stat = "identity")+
  scale_x_continuous(position = "top", 
                     expand = c(0,0), 
                     limits = c(0, 45))+
  scale_y_discrete(expand = expansion(add = c(0,0))) + 
  theme(
    # Set background color to white
    panel.background = element_rect(fill = "white"),
    # Set the color and the width of the grid lines for the horizontal axis
    panel.grid.major.x = element_line(color = "#A8BAC4", size = 0.3),
    # Remove tick marks by setting their length to 0
    axis.ticks.length = unit(0, "mm"),
    # Remove the title for both axes
    axis.title = element_blank(),
    # Only left line of the vertical axis is painted in black
    axis.line.y.left = element_line(color = "black"),
    # Remove labels from the vertical axis
    axis.text.y = element_blank(),
    # But customize labels for the horizontal axis
    axis.text.x = element_text(family = "Arial", size = 12)) + 
  geom_text(aes(x = perc, y = consv_bin, label = consv_bin),
    hjust = 0,
    nudge_x = 0.3,
    colour = "dodgerblue4",
    family = "Arial",
    size = 3.5)+
  labs(subtitle = "Percent of sum from all articles (%)") + 
  theme(plot.subtitle = element_text(
      family = "Arial",
      size = 13)
  )

@@

@@

::: panel-tabset

#### Literature

@@

![](images/survey_combo.png){fig-align="center" width="5in", height = "8in"}

:::

@@

#format data
freq_pos_survey <- code_vars_s %>% 
  select(c(6:10, 21:54)) %>% 
  janitor::clean_names() %>%
  pivot_longer(1:5, names_to = "test", values_to = "position") %>%
  select(-c(test)) %>%
  pivot_longer(1:34, names_to = "sub_theme", values_to = "total") %>%
  group_by(position, sub_theme) %>%
  summarise(total = sum(total), 
            .groups = "drop") %>%
  drop_na(position)

>>>>

consv_bar <- ggplot(consv_s) +
  geom_bar(aes(x = perc, y = reorder(consv_topic, perc)), fill = "dodgerblue4", width = 0.6, stat = "identity")+
  scale_x_continuous(position = "top", 
                     expand = c(0,0), 
                     limits = c(0, 45))+
  scale_y_discrete(expand = expansion(add = c(0,0))) + 
  theme(
    panel.background = element_rect(fill = "white"),
    panel.grid.major.x = element_line(color = "#A8BAC4", size = 0.3),
    axis.ticks.length = unit(0, "mm"),
    axis.title = element_blank(),
    axis.line.y.left = element_line(color = "black"),
    axis.text.y = element_blank(),
    axis.text.x = element_text(family = "Arial", size = 12)) + 
  geom_text(aes(x = perc, y = consv_topic, label = consv_topic),
    hjust = 0,
    nudge_x = 0.3,
    colour = "dodgerblue4",
    #family = "Arial",
    size = 3.5)+
  labs(subtitle = "Percent of sum from all articles (%)") + 
  theme(plot.subtitle = element_text(
      #family = "Arial",
      size = 13)
  )

consv_bar
#ggsave("figures/ms_figs/consv_perc/consv_bar.pdf", consv_bar, height = 5, width = 5, units = c("in"))
```

@@

consv_bar2 <- ggplot(consv_s) +
  geom_bar(aes(x = perc, y = reorder(consv_bin, perc), fill = consv_topic), width = 0.6, stat = "identity")+
  scale_x_continuous(position = "top", 
                     expand = c(0,0), 
                     limits = c(0, 45))+
  scale_y_discrete(expand = expansion(add = c(0,0))) + 
  theme(
    panel.background = element_rect(fill = "white"),
    panel.grid.major.x = element_line(color = "#A8BAC4", size = 0.3),
    axis.ticks.length = unit(0, "mm"),
    axis.title = element_blank(),
    axis.line.y.left = element_line(color = "black"),
    axis.text.y = element_blank(),
    axis.text.x = element_text(family = "Arial", size = 12)) + 
  geom_text(aes(x = perc, y = consv_bin, label = consv_bin),
    hjust = 0,
    nudge_x = 0.3,
    colour = "dodgerblue4",
    #family = "Arial",
    size = 3.5)+
  labs(subtitle = "Percent of sum from all articles (%)") + 
  theme(plot.subtitle = element_text(
      #family = "Arial",
      size = 13)
  )

@@

freq_job_survey2 %>%
  mutate(all_codes = sum(value)) %>%
  group_by(code_cat) %>%
  summarise(prop = value/all_codes)

@@

::: panel-tabset
#### Literature

@@

![](images/survey_combo.png){fig-align="center" width="5in", height = "8in"}
:::

@@

#survey figs
#format data
freq_pos_survey <- code_vars_s %>% 
  select(c(6:10, 21:54)) %>% 
  janitor::clean_names() %>%
  pivot_longer(1:5, names_to = "test", values_to = "position") %>%
  select(-c(test)) %>%
  pivot_longer(1:34, names_to = "sub_theme", values_to = "total") %>%
  group_by(position, sub_theme) %>%
  summarise(total = sum(total), 
            .groups = "drop") %>%
  drop_na(position)
